The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-06-04 manuscript/manuscript.tex
push before update on overleaf

The correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution. We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation. We take selection effect into account to fit this offset as \mbh/\smass$\propto(1+z)^\gamma$, and obtain $\gamma = 0.80\pm0.30$. Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today. This indication also exist in the \mbh-\lhost\ relation, once account for the passive evolution of the host luminosity. The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.

@@

Most galactic nuclei are thought to harbor a supermassive black hole (BH), whose mass (\mbh) is known to be correlated with the host properties, such as \mbh-host luminosity (\lhost), \mbh-stellar mass (\smass) and \mbh-stellar velocity dispersion (\sigstar). These tight correlations indicate a connection between nuclear activity and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the BHs dynamical sphere ($\sim$pc) and their host galaxy ($\sim10$ kpc). On the one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering the active galactic nucleus (AGN) feedback as the physical driver~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of physical coupling, another possibility is a statistical convergence from the galaxy mergers which reproduces the observed correlations.

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass and \mbh-\sigstar relations. \textcolor{blue}{In addition, based on spectroscopic information, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components, finding a positive evolution of black holes to the galaxies in their correlation.
This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells.
It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars and limited size of the sample. For example, some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}. In addition, once considering the selection effect \citet{Mechtley2012, Schulze2014}, the observed apparent offset at high redshift is fully consistent with no intrinsic offset.}

In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed AGNs, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
\textcolor{blue}{
In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest.}%~\citep{DeG++15}.

The paper is organized as follows. We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}. We describe the observation and collect the PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass\ and compared to the local samples. Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.

Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} =
0.70$. Magnitudes are given in the AB system.

@@

\section{Experimental design}
\label{sec:data}
%Our study overcomes the limitations of previous studies in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators. Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. 
We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.  
We design to choose our sample that meets the following criterion to overcome the limitations of previous studies.
\begin{enumerate}
\item A sample of broad-line (type-1) AGNs that fall well below the knee of the black how mass function to minimize the bias which could raised by the selection effect.
\item Sufficient Eddington ratios to assure the AGN contains accreting black hole.
\item Balmer lines are available to estimate their \mbh, which avoids potential systematic uncertainties in the UV-based estimators \citep{Greene2005}.
\item X-ray selected sample results in lower nuclear-to-host ratios facilitating the galaxy mass measurements.
\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break and below the broad \halpha\ line (6563 \angstrom) given their redshift range.
\item The large proportion of the sample has multi-band \hst\ imaging, providing extra color information to achieve reliable K-correction and stellar mass inference. 
\end{enumerate}

In redshift range $1.2<z<1.7$, we will measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e. $\sim0.23$ dex,][]{Schulze2014}.

\subsection{Target selection}
We focus on broad-line AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields, with X-ray flux limited in 0.5-8 keV.
The Near IR spectra of the AGNs in these fields are available from the survey of Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Matsuoka2013, Nobuta2012}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. More recently, \citet{Schulze2018} present near-IR spectroscopy of a large sample of 243 X-ray AGN in these field. We referred to that paper for the details of continuum fitting and emission line modeling. 
\textcolor{red}{John comments to be included:
[These were first identified through optical spectroscopy in most cases with zCOSMOS bright of faint samples (see Merloni et al. 2007) and then followed up with NIR spectroscopy.]}

Using the \mbh\ estimator introduced in Section~\ref{mbh}, we estimate the value of \mbh\ and select the targets meets range $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
The bolometric luminosities presented in \citet{Schulze2018} help us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$. We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}. Moreover, we have higher preference to select the target which has rest-frame UV images as provided by \citet{Scoville2007}.

We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.

@@

\subsection{BH masses}
\label{mbh}
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

@@

Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. {\color{blue} 3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha emission line, to assure they are self-consistent.
%Given that 18/32 sample are lack of \hbeta\ line, we thus adopt the \mbh\ estimated by \halpha\ to our sample in the rest of the work, to avoid the scatter of the \mbh\ by \hbeta\ unevenly spreading into the overall sample.

@@

\section{\hst\ observations}
\label{observation}
%\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. For this purpose, all the new 32 AGN systems were observed with the \hst/WFC3 infrared channel, as part of the HST program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calculations.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff$\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$). We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
We also test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
}}.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift.}
\end{figure*}

@@

Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios. The inference could be biased, when extending the selected sample to the global without properly considering the selection effect~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}. In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than the random ones, highlighting the necessity of eliminating the selection biases.

\textcolor{red}{To be updated with Andres's result.}
We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}. Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work. We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear. According to the observed distribution, we consider the observational selection of \mbh\ of our samples by lower and upper limits of $[7.7, 8.8]$ to model their distribution. To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity. In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).

@@

@@

{\color{blue}
\subsection{The origin of the offset}
We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift. We consider if the offset is related to the AGN activities. The straightforward way is to study such offset, i.e. $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}. Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh. However, at higher Eddington ratio, the offset turns to be lower.
 {\color{red} Some interpretations need to be presented.}

>>>>

The correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful test of this co-evolution hypothesis is to measure the relations \mbh-\lhost\ and \mbh-\smass~(total) at high redshift and compare with the local relation. For this purpose, we obtained multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ emission, we obtained accurate measurements of the host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on near-infrared spectroscopic observations of the broad \halpha~line, which avoids potential uncertainties associated with \Mgii\ or \Civ\ .
%We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution. 
We find that the observed ratio of \mbh/\smass ~is 0.0035, a 0.24~dex offset as compared to the local relation that would lead to a evolution as \mbh/\smass$\propto(1+z)^\gamma$ with $\gamma = 0.80\pm0.30$. However, we expect an offset of 0.21 dex at these redshifts due to a selection bias thus the high-$z$ sample is consistent with the local sample if considering this effect. This is in agreement with the lack of evolution seen in the \mbh/\lhost ~ratios of our sample. Therefore, our results depict a scenario where SMBHs and their host galaxies co-evolve with the possibility for SMBHs to have slightly elevated masses, considering the observed ratios, that may indicate that galaxies with lower angular momentum at high-$z$ may be a bit more efficient to grow their black holes at earlier cosmic times. In any case, the bulge \smass ~mass at a given black hole mass is clearly discrepant with the local relation, since the hosts have a significant amount of stellar mass in a disk, thus leaving the open question as to whether the connection to the bulge is relevant for black hole growth.

@@

Most galactic nuclei are thought to harbor a supermassive black hole (SMBH), whose mass (\mbh) is known to be correlated with the host properties, such as luminosity (\lhost), stellar mass (\smass) and stellar velocity dispersion (\sigstar). These tight correlations may indicate a connection between nuclear activity, and galaxy formation and evolution~\citep[e.g.,][]{Mag++98, F+M00, M+H03, Gul++09,Beifi2012, H+R04, Geb++01b, Gra++2011}.
Currently, the physical mechanism that can produce such a tight relationship is unknown, due to the daunting range of scales between the dynamical sphere ($\sim$pc) of the SMBH and their host galaxy ($\sim10$ kpc). On one hand, cosmological simulations of structure formation are able to reproduce the mean local correlations considering {\color{blue} either the active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or how the growth of these components is connected to the common gas supply~\citep{Cen2015, Menci2016}}.
On the other hand, \citet{Peng2007, Jahnke2011, Hirschmann2010} show that, without the need of a physical coupling, another possibility is a statistical convergence from galaxy assembly (i.e., mergers) which can reproduce the observed correlations.

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015}. During the past decade, there has been much progress on this front at $z<1$ using type-1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. Similarly, the works by \citet{Bennert11, Woo++08} find the positive evolution of \mbh\ in the observation of the \mbh-\smass\ and \mbh-\sigstar\ relations. Of similar results, \citet{Merloni2010} decomposed the entire spectral energy distributions (SED) into a nuclear AGN and host-galaxy components and found a positive evolution of the mass ratios of black holes to their host galaxies; although, the accuracy of such an approach has not yet been well established. If realized, such offsets can be interpreted as a scenario in which SMBHs were built up first with galaxies then growing around their deep potential wells.

However, there are studies \citep{Cisternas2011,SS13,Mechtley2012} based on \hst\  imaging of deep survey fields such as COSMOS and CDFS that report no evolution in the \mbh - \smass ~ mass ratio as compared to the local relation. In support, \citet{Sun2015} has re-analyzed the mass ratios for BLAGN in the COSMOS field in a similar manner (i.e., stellar mass measurements from SED fitting) to \citep{Merloni2010} and finds no evolution when accounting for selection effects \citep{Schulze2014} that consider the black hole mass functions and Eddington rate distribution. As highlighted below, samples based on 2D image analysis using \hst\ at $z>1$ are limited thus the infrared capabilities of \hst/WFC3 have not been fully exploited to date on this topic.

In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed AGNs, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.

%~\citep{DeG++15}.
%We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch close to the peak in the accretion history of SMBHs~\citep[e.g.,][]{Aird2015}.

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to the highest redshifts where evolutionary effects should be strongest. In particular, we measure the properties of 32 host galaxies in redshift range $1.2<z<1.7$ using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e. $\sim0.23$ dex,][]{Schulze2014}. The paper is organized as follows. We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}. We describe the observation and collect the PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass\ and compared to the local samples. Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}. Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are given in the AB system.

@@

\section{Experimental design}
\label{sec:data}
%Our study overcomes the limitations of previous studies in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators. Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference.

We construct a sample of broad-line (FWHM$>2000$ km s$^{-1}$; type-1) AGNs that meet the following criterion to overcome limitations of previous studies.

\begin{itemize}

\item Black hole mass estimates (\mbh) are based on Balmer lines (i.e., H$\alpha$) which avoids potential systematic uncertainties in UV-based estimators \citep{Greene2005}.

\item Black holes masses fall below the knee of the black hole mass function to minimize the selection biases.

\item Eddington ratios typically above 1\% for most of the sample.

\item A X-ray selected sample demonstrated to have lower nuclear-to-host ratios thus facilitating the galaxy mass measurements.

\item \hst/WFC3 imaging of the host galaxy above the 4000~\angstrom\ break and not including the broad \halpha\ line (6563~\angstrom).

\item The large fraction of the sample has addition \hst\ imaging (i.e., \hst/ACS, providing extra color information to achieve reliable K-corrections and stellar mass determinations. 
\end{itemize}

\subsection{Target selection}

The AGN sample is initially detected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. More recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. We refer the reader to that paper for the details of continuum fitting and emission-line modeling.

Using the \mbh\ estimates as described below (Section~\ref{mbh}), we select targets with masses between $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$. The bolometric luminosities presented in \citet{Schulze2018} are used to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$. We are able to select the sample which have higher Eddington ratios when \mbh\ is lower, to assure the AGN is still activate, as shown in Figure~\ref{fig:selection}. Moreover, we have higher preference to select targets which have rest-frame UV images as provided by \citet{Scoville2007}. We list all the AGN systems analyzed in this work (Table~\ref{tab:objlist}).

@@

\subsection{Details on BH mass estimates}
\label{mbh}
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

@@

Having defined the recipes, we estimate \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. {\color{blue} 3/32 systems, including CDFS-1, CDFS-229 and CDFS-724, are not included in \citet{Schulze2018}; their \halpha\ emission lines information is provided by \citet{Suh2015}.
14/32 systems have both \halpha\ and \hbeta\ emission line information. However, we only adopt the value for \mbh\ using the \halpha\ emission line, to assure they are self-consistent.
%Given that 18/32 sample are lack of \hbeta\ line, we thus adopt the \mbh\ estimated by \halpha\ to our sample in the rest of the work, to avoid the scatter of the \mbh\ by \hbeta\ unevenly spreading into the overall sample.

@@

\section{\hst\ observations}
\label{observation}
%\subsubsection{HST image Observation}
% The AGN surface photometry in IR Channel Filters.\\
High spatial resolution imaging is required for the decomposition of the nuclear/host emission and the accurate estimate of the host stellar mass. For this purpose, all the new 32 AGN systems were observed with the \hst/WFC3 infrared channel, as part of the \hst\ program GO-15115, PI: John Silverman. We selected to use the filters F125W $(1.2<z<1.44)$ and F140W $(1.44<z<1.7)$ according to the redshift of the targets. This selection ensures that the broad \halpha\ line is not present in the bandpass so as not to contaminate the host emissions due to the broad wings of the PSF.

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calculations.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$). We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
We test to use $n\in[1,4]$ as prior, and find that the changes on the inference of the host properties are very limited.
}}.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift. We use open green circle to show the expected shifting of the median offset value before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.
}
\end{figure*}

@@

Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios. The inference could be biased, when extending the selected sample to the global without properly considering the selection effect~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}. In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than the random ones, highlighting the necessity of eliminating the selection biases. {\color{blue} We consider the selection effect using two independent approach introduced in the following two subsections.

\subsubsection{Test selection effect using Monte Carlo simulation}
We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}. Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work. We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear. According to the observed distribution, we consider the observational selection of \mbh\ of our samples by their lower and upper limits to model their distribution. To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity. In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).

@@

\subsubsection{Test selection effect using Bayesian framework} \label{sec:sf_framework}
We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by the selection window and local sample that we adopted. The framework considers the fact that, with the particular selection window, the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation. Moreover, the other relevant sources of bias are considered, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.

Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, their is an expected bias of 0.21~dex in the inference of $\Delta\log($\mbh$)$ for samples at $z\sim1.5$. Interestingly, this bias could account for the offset that obtained in Section~\ref{sec:mm}. We use open green circle to point out the shifting of the expected population given the biases in Figure~\ref{fig:MM-vz}.

Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.

@@

{\color{blue}
\subsection{The origin of the offset}
{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present this?]}
We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift. We consider if the offset is related to the AGN activities. The straightforward way is to study such offset, i.e. $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}. Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh. However, at higher Eddington ratio, the offset turns to be lower.
 {\color{red} Some interpretations need to be presented.}
